
---
title: "Germination Analysis under Salinity Stress"
author: "Isaac Koomson"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
```

## 📥 Load Dataset

```{r}
data <- read_csv("datasets/seed_germination_stress.csv")
head(data)
```

## 📊 Calculate Germination Percentage

```{r}
data <- data %>%
  mutate(Germination_Percent = (Germinated_Seeds / Total_Seeds) * 100)
```

## 📈 Summary Statistics per Treatment

```{r}
summary_stats <- data %>%
  group_by(Treatment) %>%
  summarise(
    Mean = mean(Germination_Percent),
    SD = sd(Germination_Percent),
    SE = SD / sqrt(n()),
    CV = (SD / Mean) * 100
  )
summary_stats
```

## 📦 Boxplot: Germination Percentage by Salinity Treatment

```{r}
ggplot(data, aes(x = Treatment, y = Germination_Percent, fill = Treatment)) +
  geom_boxplot() +
  labs(title = "Effect of Salinity on Germination", y = "Germination (%)") +
  theme_minimal() +
  theme(legend.position = "none")
```

## 🧠 Biological Interpretation

The plot and statistics show that increasing salinity levels reduce germination percentages. At 2.0 dS/m, germination drops below 40%, indicating strong salinity stress. Control treatments maintain nearly 100% germination.

---

## 🧪 Next Steps (Phase 1.2)

- Perform ANOVA to compare treatments
- Run Tukey HSD test
- Visualize group differences with letters
